In today's digital landscape, data has become complex and bulky as it continues to 
grow from independent sources. In fact, there is so much data available that the 
term ``Big Data`` has become regularly used across industries with data analytics as a 
driving force behind innovation. For companies hoping to leverage datasets, fully
understanding them is key to effectively create strategic advantages in their respective 
industries. In a typical workflow, the data preprocessing step is the ideal time 
where organizing the data into a meaningful form so that a trend, if any, emerging 
out of the data can be recognized and further analyzed \cite{c10}. 

One of the most common methods used for organizing data are frequency distributions.
A frequency distribution which is an overview of all the distinct values in some 
variable and the number of times they occur is a standard visualization technique. 
In practice frequency distributions are most commonly used to summarize categorical 
variables in datasets. If constructed well a frequency distribution is sometimes 
enough to make a detailed analysis of the structure of a population with respect 
to a given characteristic. Furthermore, one can easily spot whether observations 
are high or low and concentrated in one area or spread out across the entire scale. 
In this paper, we will briefly discuss some of the basic characteristics of 
frequency distributions and the visualization techniques available to 
illustrate them along with their strengths and weaknesses.
